Comparison of MCMC algorithms in Stochastic Volatility Models

### 2023-09-25 manuscript/main.tex
Updated captions

\documentclass[12pt, a4paper]{article}
\setcounter{tocdepth}{2}
\usepackage{graphicx} % Required for inserting images
\usepackage[parfill]{parskip} % Removes indent from new paragraphs
\usepackage{amsmath, amssymb, amsfonts}
\usepackage[colorlinks = true,
			citecolor  = blue,
            linkcolor = black]{hyperref}
\usepackage[font={small,it}]{caption}
\usepackage[labelfont=bf]{caption}

@@

    \begin{figure}[h]
        \centering
        \includegraphics[scale=0.1]{motivating_example/real_data_ex.png}
        \caption{Posterior samples from two MCMC algorithms using S\&P 500 data}
    \end{figure}

    These estimates show the marginal posteriors of each parameter sharing similar shapes. $\phi$  has a fatter left tail for and $\sigma^2$ has heavier right tails for sampling method 1 (SM1). Furthermore, SM2 has higher peaks at their mode relative to SM1 with a tighter spread. Based on this information alone, there is no certainty in whether SM1 or SM2 is has a more correct estimate conditional on data and model. There are other methods for model or algorithmic selection in this context (for example, out of sample predictive performance), but for parameter estimation it is unclear which one should be selected.

@@

    The below results are from a single simulation where data is generated and sampled from the stochastic volatility model with known parameters.

    \begin{figure}[h]
        \centering
        \includegraphics[scale=0.1]{motivating_example/single_sim.png}
        \caption{Posterior samples from known data genearting process. Vertical solid line represents true parameter and dotted lines are 95\% credible intervals around the mean}
    \end{figure}

@@

    \subsection{Hamiltonian Monte Carlo}

    \subsection{Gaussian Mixture Approximation}

@@

\subsection{Limitations}

>>>>

\documentclass[12pt, a4paper]{article}
\setcounter{tocdepth}{2}
\usepackage{graphicx} % Required for inserting images
\usepackage[parfill]{parskip} % Removes indent from new paragraphs
\usepackage{amsmath, amssymb, amsfonts}
\usepackage[colorlinks = true,
			citecolor  = blue,
            linkcolor = black]{hyperref}
\usepackage[font={small,it}]{caption} % Figure caption font
\usepackage[labelfont=bf]{caption} % Bold figure x.x

@@

    \begin{figure}[h]
        \centering
        \includegraphics[scale=0.1]{motivating_example/real_data_ex.png}
        \caption{Posterior samples from two MCMC algorithms using S\&P 500 data. While the shape of the distributions are similar, the modes of method 2 is much higher and the tails of method 1 are fatter for $\phi$ and $\sigma^2$. Convergence diagnostics do not tell us which estimate is "more correct" since we don't observe the true model or true data generating process.}
    \end{figure}

    These estimates show the marginal posteriors of each parameter sharing similar shapes. $\phi$  has a fatter left tail for and $\sigma^2$ has heavier right tails for sampling method 1. Furthermore, sampling method 2 has higher peaks at their mode relative to method 1 with a tighter spread. Based on this information alone, there is no certainty in whether method 1 or method 2 is has a more correct estimate conditional on data and model. There are other methods for model or algorithmic selection in this context (for example, out of sample predictive performance), but for parameter estimation it is unclear which one should be selected.

@@

    Figure 2 show the posterior distributions of a single simulation where data is generated and sampled from the stochastic volatility model with known parameters.

    \begin{figure}[h]
        \centering
        \includegraphics[scale=0.1]{motivating_example/single_sim.png}
        \caption{Posterior samples from known data genearting process. Vertical solid line represents true parameter and dotted lines are 95\% credible intervals around the mean. The parameter $\phi$ falls outside the credible interval whereas $\mu$ and $\sigma^2$ stay inside. In any one simulation conditional on the correct model, there is a 5\% probability that the true parameter falls outside this interval by chance.}
    \end{figure}

@@

    \subsection{Centered paramterisation}

    \subsubsection{Hamiltonian Monte Carlo}

    \subsubsection{Gaussian Mixture Approximation}

    \subsection{Reparameterised models}

    \subsubsection{Hamiltonian Monte Carlo}

    \subsubsection{Gaussian Mixture Approximation}

@@

\subsection{Limitations}
- SBC is computationally expensive.

- Datasets generated dependent on the priors. If priors are diffuse then can get a wide set of possible datasets which make it harder to get calibrated estimates of the true parameter.
